Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-01 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added details to color scheme, sidebar, paper pres, role models

\documentclass[10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}

@@

%\usetheme{Boadilla}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\usetheme[right]{Berkeley}
\setbeamercolor{sidebar}{bg=blue}

@@

\title[Skills, Practices, and Aspirations of Small Firms in LMICs]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
\author[R{\"u}schenp{\"o}hler]{Julius R{\"u}schenp{\"o}hler\inst{*}}
\institute[]{\inst{*} UC Berkeley, CEGA}
\date{March 04, 2021}

@@

@@

%\begin{frame}
%\frametitle{Overview of the Lecture}
%\tableofcontents[hideallsubsections]
%\end{frame}

\AtBeginSection
{\begin{frame}{Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}}

%\begin{document}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Business practices, motivation
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Value-Added of Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Correlation with productivity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Heterogeneity and predictiveness
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Example categories and practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize}
	\item At least \textcolor{red}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
	\vspace{0.1in}
	\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
	\vspace{0.2in}
	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item First wave (Karlan and Valdivia, 2011, etc.)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Education}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%\setbeamertemplate{sidebar right}{}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

@@

\title[Curating Local Knowledge]{Curating Local Knowledge}
\subtitle{Experimental Evidence from Small Retailers in Indonesia}

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}}

\institute[]{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank}

@@

%\setbeamertemplate{sidebar right}{}

@@

%------------------------------------------------
\section{Background}

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize}
\item \textbf{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); Drexler, Fischer \& Schoar (2014); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.2in}
\item \textbf{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.2in}

@@

\begin{frame}
\frametitle{What We Do}
\begin{itemize}
\item Some facts about business practices in firms:
	\begin{itemize}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize}
\vspace{0.2in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.2in}
\pause
\item Our idea is to make it \textbf{central} to the research design: 
	\begin{itemize}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize}
\end{itemize}

@@

%
\begin{frame}
\frametitle{How Do We Share this Knowledge?}
		\begin{itemize}
		\item \textbf{Handbook}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textbf{Positive Frame}: Retailers who implement [x] report y\% \textbf{higher} sales and z\% \textbf{higher} profits.
            %\item \textbf{Negative Frame}: Retailers who do \textbf{not} implement [x] report y\% \textbf{lower} sales and z\% \textbf{lower} profits.
			\end{itemize}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textbf{Movie}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textbf{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize}

\bigskip
		\item \textbf{In-shop Light Assistance}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
			\end{itemize}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize}

@@

@@

\section{Data and Analysis}

@@

\begin{frame}
\frametitle{Efficiency Gains?}
\begin{enumerate}
\item Unpacking impacts on practices shows improvements in efficiency practices:
\vspace{0.1in}
\begin{itemize}
\item Adjust stocks based on product profitability
\item Negotiate lower prices with suppliers
\item Consult with former customers
\item Offer discounts
\item Make joint decisions
\item Review financial performance to identify channels of improvement
\item Make anticipated budget for upcoming costs
\end{itemize}
\vspace{0.2in}
\pause
\item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
\vspace{0.2in}
\pause
\item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
\end{enumerate}
\vspace{0.2in}
$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Efficiency gains}
\end{frame}

@@

\begin{frame}
\frametitle{Cost-Effectiveness}
\begin{itemize}
\item \textbf{Low cost} per firm:
\begin{itemize}
\item Cost Handbook alone: USD 100
\item Cost Handbook \& Movie: USD 125
\item Cost Handbook \& Assistance: USD 125
\item Cost Handbook \& Assistance \& Movie: USD 150
\vspace{0.20in}
\end{itemize}
\item \textbf{High Benefits}
    \begin{itemize}
    \item Up to USD 330 per month in profits.
    \item Adoption of top practices by retailers.
    \end{itemize}
\vspace{0.20in}
 \item Research Design \textbf{scalable and replicable} in other settings.
\end{itemize}
\end{frame}

%--------------------------------------
\begin{frame}
\frametitle{Takeaways}
\begin{itemize}
    \item Curating local knowledge has value for business growth 
            \vspace{0.20in}
    \item Knowledge alone does not have an impact but needs additional help or nudges
            \vspace{0.20in}
	\item These "add-ons" are inexpensive and scalable, making this type of intervention very attractive for policy

@@

>>>>

\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}

@@

% Color scheme and sidebar
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
\definecolor{bluemunsell}{rgb}{0.0, 0.5, 0.69}
%#09BADB #DB1A71
\usetheme[right]{Berkeley}
\setbeamercolor{palette primary}{bg=ceruleanblue,fg=white}
\setbeamercolor{palette secondary}{bg=bleudefrance,fg=white}
%\setbeamercolor{sidebar}{bg=bleudefrance}

% Mini frames
%\useoutertheme[subsection=true]{miniframes}

@@

\title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
\author[]{Julius R{\"u}schenp{\"o}hler\inst{*}}
\institute[]{\inst{*} UC Berkeley, CEGA}
\date{March 04, 2021}

@@

% Create generic TOC

%\AtBeginSection
%{\begin{frame}{Overview}
%\tableofcontents[currentsection,hideothersubsections]
%\end{frame}}

@@

\begin{frame}{Lecture Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Value-Added of Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2019): Correlation with productivity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize}
	\item At least \textcolor{bleudefrance}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
	\vspace{0.1in}
	\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
	\vspace{0.2in}
	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize}
	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Education}
	\begin{itemize}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

@@

\title[]{Curating Local Knowledge}
\subtitle{Experimental Evidence from Small Retailers in Indonesia}

\author[]
{Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}}

\institute[]{
\inst{1} Tilburg University\\
\bigskip
\inst{2} UC Berkeley, CEGA\\
\bigskip
\inst{3} The World Bank}

@@

@@

\begin{frame}{Paper Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}

%------------------------------------------------
\subsection{Motivation}

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize}
\item \textbf{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.2in}
\item \textbf{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.2in}

@@

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
\begin{itemize}
\item Some facts about business practices in firms:
	\begin{itemize}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize}
\vspace{0.2in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.2in}
\pause
\item Our idea is to make it \textbf{central} to the research design: 
	\begin{itemize}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize}
\end{itemize}

@@

%
\begin{frame}
\frametitle{Disseminating Knowledge}
		\begin{itemize}
		\item \textbf{Handbook}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textbf{Positive Frame}: Retailers who implement [x] report y\% \textbf{higher} sales and z\% \textbf{higher} profits.
            %\item \textbf{Negative Frame}: Retailers who do \textbf{not} implement [x] report y\% \textbf{lower} sales and z\% \textbf{lower} profits.
			\end{itemize}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textbf{Movie}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textbf{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize}

\bigskip
		\item \textbf{In-shop Assistance}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
			\item Facilitated by local lay person
			\end{itemize}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize}

@@

\subsection{Data and Design}

@@

\subsection{Results}

@@

\subsection{Discussion}
\begin{frame}
\frametitle{Efficiency Gains?}
\begin{enumerate}
\item Unpacking impacts on practices shows improvements in efficiency practices:
\vspace{0.1in}
\begin{itemize}
\item Adjust stocks based on product profitability
\item Negotiate lower prices with suppliers
\item Consult with former customers
\item Offer discounts
\item Make joint decisions
\item Review financial performance to identify channels of improvement
\item Make anticipated budget for upcoming costs
\end{itemize}
\vspace{0.2in}
\pause
\item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
\vspace{0.2in}
\pause
\item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
\end{enumerate}
\vspace{0.2in}
$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Efficiency gains}
\end{frame}

@@

\begin{frame}
\frametitle{Cost-Effectiveness}
\begin{itemize}
\item \textbf{Low cost} per firm:
\begin{itemize}
\item Cost Handbook alone: USD 100
\item Cost Handbook \& Movie: USD 125
\item Cost Handbook \& Assistance: USD 125
\item Cost Handbook \& Assistance \& Movie: USD 150
\vspace{0.20in}
\end{itemize}
\item \textbf{High Benefits}
    \begin{itemize}
    \item Up to USD 330 per month in profits.
    \item Adoption of top practices by retailers.
    \end{itemize}
\vspace{0.20in}
 \item Research Design likely \textbf{scalable and replicable} in other settings.
\end{itemize}
\end{frame}

\subsection{Conclusion}
\begin{frame}
\frametitle{Takeaways}
\begin{itemize}
    \item Curating local knowledge has value for business growth 
            \vspace{0.20in}
    \item Information alone does not have impact, but behavioral interventions are needed
            \vspace{0.20in}
	\item These "add-ons" are inexpensive and scalable, making this type of intervention very attractive for policy

@@

%\bibliographystyle{econometrica}
%\bibliography{sampleBibFile}
